Verification of Stencil Computations with Spatial Specifications

### 2016-10-15 new-intro.tex
Add citation to Kamil et al.

We provide a verification tool for such specification which can check
the correctness of code against the specification, and can also infer
specifications, synthesising these as comments in the
source code. The main features and benefits of our approach are as follows:
%
\begin{itemize}
\item The main use case is that a programmers writes a specification
  first (perhaps informed by their numerical analysis), then writes
  the corresponding source code, and lastly has the tool check its
  conformance to the specifications. This specify-and-check approach
  removes the usually ad hoc testing effort, and provides the
  opportunity for easy re-verification in the event of any refactoring
  of software maintenance activities.
%
\item The specification provides a concise description which can be
  preserved in the source code to provide documentation to future
  developers, contrasting with ad hoc tests which are usually
  discarded or specialised to the development environment. Separate from the
  verification procedure, the infer-and-synthesise mode of the tool
  provides a way to automatically generate additional useful
  documentation for future users.
%
\item Specifications are integrated into the code as comments for easy
integration with existing tools, as well as
  documentation systems (\eg{}, we support Doxygen syntax).
%
\item Our specification format is deliberately abstract, with a small
  number of combinators that \emph{do not involve any indexing
    expressions}, \eg{} does not involve expressions like
  \texttt{a(i+1,j-1)}. This contrasts with other stencil specification
  approaches. For example, the work of Kamil et al. provides
  full-functionality specifications of stencil computations from which
  equivalent DSL code can be generated.  If a user wishes to specify,
  say, the Naiver-Stokes stencil above, they must write a
  specification which is very similar, involving textually dense
  array-indexing expressions. Therefore any low-level mistakes that
  could be made programming complex indexing code could also be made
  when writing a specification. Our specifications are much more
  abstract, and also more lightweight with the aim of aiding adoption
  by scientists.
\end{itemize}

>>>>

We provide a verification tool for such specification which can check
the correctness of code against the specification, and can also infer
specifications, synthesising these as comments in the
source code. The main features and benefits of our approach are as follows:
%
\begin{itemize}
\item The main use case is that a programmers writes a specification
  first (perhaps informed by their numerical analysis), then writes
  the corresponding source code, and lastly has the tool check its
  conformance to the specifications. This specify-and-check approach
  removes the usually ad hoc testing effort, and provides the
  opportunity for easy re-verification in the event of any refactoring
  of software maintenance activities.
%
\item The specification provides a concise description which can be
  preserved in the source code to provide documentation to future
  developers, contrasting with ad hoc tests which are usually
  discarded or specialised to the development environment. Separate from the
  verification procedure, the infer-and-synthesise mode of the tool
  provides a way to automatically generate additional useful
  documentation for future users.
%
\item Specifications are integrated into the code as comments for easy
integration with existing tools, as well as
  documentation systems (\eg{}, we support Doxygen syntax).
%
\item Our specification format is deliberately abstract, with a small
  number of combinators that \emph{do not involve any indexing
    expressions}, \eg{} does not involve expressions like
  \texttt{a(i+1,j-1)}. This contrasts with other stencil specification
  approaches. For example, the work of Kamil et al.~\cite{kamil2016verified}
  provides full-functionality specifications of stencil computations from which
  equivalent DSL code can be generated.  If a user wishes to specify, say, the
  Naiver-Stokes stencil above, they must write a specification which is very
  similar, involving textually dense array-indexing expressions. Therefore any
  low-level mistakes that could be made programming complex indexing code could
  also be made when writing a specification. Our specifications are much more
  abstract, and also more lightweight with the aim of aiding adoption by
  scientists.
\end{itemize}
